Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae

### 2020-11-14 introduction.tex
Update introduction.tex
Fixed typo

In the last decade significant progress has been made in the development of numerical codes, {in particular in the treatment of multidimensioal effects \citep{BMueller:2020}.} In the case of  neutrino-driven explosions, the GW emission is {primarly induced by instabilities developed at the newly formed proto-neutron star (PNS) and by the non-spherical accreting flow of hot matter over its surface \citep{Kotake:2017}.  These} dynamics excite the different modes of oscillation of the PNS which ultimately leads to the emission of GWs. The frequency and time evolution of these modes carry information about the properties of the GW emitter and could allow to perform PNS asteroseismology.

>>>>

In the last decade significant progress has been made in the development of numerical codes, {in particular in the treatment of multidimensional effects \citep{BMueller:2020}.} In the case of  neutrino-driven explosions, the GW emission is {primarly induced by instabilities developed at the newly formed proto-neutron star (PNS) and by the non-spherical accreting flow of hot matter over its surface \citep{Kotake:2017}.  These} dynamics excite the different modes of oscillation of the PNS which ultimately leads to the emission of GWs. The frequency and time evolution of these modes carry information about the properties of the GW emitter and could allow to perform PNS asteroseismology.
